clusters

### 2015-07-22 cluster.rmd
again

all7d<- all7c %>% select(mlsto, inv.mlsto, timespan, no.users, Discipline, pc.pro, 
                         client.totinv, code.director, 
                         Num.disc, Business,
                         Biz.type, code.contact, pc.majpos,
                         code.client, Project.Value, JD.Second, Post.Code, code.ProjEng, 
                         Billing.Type, majority.pos, return.pdol, cost.mlsto, hrs.mlsto)

@@

inv.knn<- function(df= all7d, predict= 'inv.mlsto', new.cases= c(1000), k=3){
        inv.knn = knn(df[,predict], df[new.cases,predict],
                df$pc.pro, k=k)
        indices<- attr(inv.knn,  "nn.index")
        #checkout the nearest neigbours!
        df %>% slice(c(new.cases,indices[1,])) %>% print

@@

inv.knn(df= all7d, predict= 'inv.mlsto', new.cases= 2000, k=3)

@@

@@

inv.knn<- function(df= all7d, predict= 'inv.mlsto', new.cases= c(1000), k=3){
        inv.knn = knn(df[,predict], df[new.cases,predict],
                df$pc.pro, k=k)
        indices<- attr(inv.knn,  "nn.index")
        #checkout the nearest neigbours!
        df %>% slice(c(new.cases,indices[1,])) %>% print

@@

inv.knn(df= all7d, predict= 'inv.mlsto', new.cases= 2000, k=3)

@@

>>>>

all7d<- all7c %>% select(mlsto, inv.mlsto, timespan, no.users, Discipline, pc.pro, 
                         client.totinv, code.director, 
                         Num.disc, Business,
                         Biz.type, code.contact, pc.majpos,
                         code.client, Project.Value, JD.Second, Post.Code, code.ProjEng, 
                         Billing.Type, majority.pos, return.pdol, cost.mlsto, hrs.mlsto, balance.mlsto)
all7d$mlsto<- as.character(all7d$mlsto)

@@

inv.knn<- function(df= all7d, predict= 'inv.mlsto', new.cases= c(1000), k=3){
        inv.knn = knn(df[,predict], df[new.cases,predict],
                df$pc.pro, k=k)
        indices<- attr(inv.knn,  "nn.index")
        #checkout the nearest neigbours!
        df %>% slice(c(new.cases, indices[1,])) %>% return

@@

a<-inv.knn(df= all7d, predict= 'inv.mlsto', new.cases= 2000, k=3)

@@

#NA values don't work in knn function so turn all NA into zeroes
knn.binary[is.na(knn.binary)]<- 0
knn.binary$pc.pro<- all7d$pc.pro

@@

cat.knn<- function(df= all7d, predict= 'inv.mlsto', new.cases= c(1000), k=3, result.df= all7d){
        inv.knn = knn(df[,predict], df[new.cases,predict],
                df$pc.pro, k=k)
        indices<- attr(inv.knn,  "nn.index")
        dists<- attr(inv.knn, 'nn.dist') %>% t %>% as.data.frame %>% round(2)
        #checkout the nearest neigbours!
        final = cbind(result.df %>% slice(c(indices[1,])), dists)
        colnames(final)[names(final) %in% 'V1']<-'knn.dist'
        return(final)

@@

b<- cat.knn(df= knn.binary, predict= colnames(knn.binary), new.cases= 60, k=5, result.df= all7d)

@@

Combine two knn results

```{r combine_knn, echo=FALSE}

b<- cat.knn(df= knn.binary, predict= colnames(knn.binary), new.cases= 60, k=20, result.df= all7d)
c<- inv.knn(df= b, predict= 'inv.mlsto', new.cases= 1, k=4) %>% slice(-1)
c
